---
title: "22 - R Markdown - Part 2"
output: 
  html_document:
    theme:  sandstone
    df_print: paged
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
---

# Side-by-Side Figures

<span style="color: green;">Utilizing par function we display images side by side below as well as priting this text in color using span html element. </span>


```{r fig.show='hold', out.width="50%", warning=FALSE}

xvec1<- c(seq(from=0,to=100))
xvec2<- c(seq(from=0,to=100))
yvec1<- c(seq(from=378,to=478))
yvec2<- c(seq(from=987,to=887))

# left image
plot(xvec1,yvec1)

# right image
plot(xvec2,yvec2)
```

# Condensed Data frame

```{r message=FALSE, warning=FALSE}  
library(tidyverse)
airquality

```

# Tabs {.tabset}
<span style="color: green;"> Utilizing tabs function we create 4 tabs to show data about health checkup as well as printing this text in color using span html element. </span>


## tab 1

Weight measured as 75kgs

## tab 2 

Height measured as 175cm

## tab 3

Body fat percentage calculated as 16.7%

## tab 4

Resulting BMI is 24.5

# Themes

<span style="color: green;"> We have applied sandstone theme from bootswatch in this html document using theme in YAML header </span>

# HTML Widgets

## datatables

<span style="color: green;"> Utilizing html widgets and DT package we created an interactive, scrollable and searchable data table </span>

```{r warning=FALSE}
library(DT)
datatable(iris, options = list(pageLength = 5))
```

# Embedded source code available for download

[Git Hub repository URL](https://github.com/anishpandey164/STAT-6020-source-files)